---
title: "Running simulations"
author: "Hector Roux de Bézieux"
date: '`r format(Sys.time(), "%d %B , %Y")`'
output:
  pdf_document
---

```{r packages, include=F}
library(knitr)
opts_chunk$set(
  fig.pos = "!h", out.extra = "", warning = FALSE, message = FALSE,
  fig.width = 5, fig.align = "center", echo = TRUE
)
if (!"DailyHRB" %in% installed.packages()) {
  devtools::install_github("HectorRDB/DailyHRB")
}
libs <- c("here", "purrr", "DailyHRB")
suppressMessages(
  suppressWarnings(sapply(libs, require, character.only = TRUE))
)
rm(libs)
```

# Loading the data and the scripts.

```{r}
sample_data <- read.csv(here("data", "sample_ga_data_binomial_2019-04-26.csv"))
source(here("R", "sim_variables.R"))
source(here("R", "ga_gbm_function.R"))
source(here("R", "vimshift_ph290_project.R"))

concordance <- function(l1, l2) {
  con <- map_dbl(1:length(l1), function(i) {
    sum(names(l1[1:i]) %in% names(l2[1:i]))}
  )
  return(sum(con))
}
```

# Impact of n on results

The idea would be to repeat this over many iterations, changing the seed in the __simulate_outcome_ function everytime.
This explains how to do one run.

```{r}
results <- map_df(7:15, function(k) {
  n <- 2^k
  print(k)
  sim1 <- simulate_outcome(sample_data = sample_data, n = n, 
                           complexity = 0, seed = sample(1:10000, 1))
  trueOrder <- ranking_complex(ranking_info = sim1$ranking_info)
  gbOrder <- gbm(data = data.frame(sim1$covariates, y = sim1$y))
  vimshiftOrder <- run_combined_var_imp(train = data.frame(sim1$covariates,
                                                           y = as.integer(sim1$y)),
                                        Wnames, Wnames_cat)
  return(concordance(sort(trueOrder, decreasing = TRUE),
                     sort(gbOrder, decreasing = TRUE)),
         concordance(sort(trueOrder, decreasing = TRUE), vimshiftOrder))
})
```

# Impact of the complexity on results

Likewise, it would great to see the impact of complexity on the results. This would need to be done over many runs as well, changing the seed.

```{r}
results <- map_df(0:10, function(i) {
  print(i)
  sim1 <- simulate_outcome(sample_data = sample_data, n = 1000, 
                           complexity = i)
  trueOrder <- ranking_complex(ranking_info = sim1$ranking_info)
  gbOrder <- gbm(data = data.frame(sim1$covariates, y = sim1$y))
  vimshiftOrder <- run_combined_var_imp(train = data.frame(sim1$covariates,
                                                           y = as.integer(sim1$y)),
                                        Wnames, Wnames_cat)
  return(concordance(trueOrder, gbOrder),
         concordance(trueOrder, vimshiftOrder))
})
```

